\documentclass{article}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{xcolor}

% Define custom colors
\definecolor{promptblue}{RGB}{41, 98, 150}
\definecolor{promptbg}{RGB}{240, 247, 255}
\definecolor{promptborder}{RGB}{100, 160, 220}

\newtcolorbox{promptframebox}[1][]{
    colback=promptbg,
    colframe=promptborder,
    coltitle=white,
    fonttitle=\bfseries\large,
    title={\textcolor{white}{Literature Review Prompt Template}},
    colbacktitle=promptblue,
    boxrule=1.5pt,
    arc=4mm,
    left=12pt, right=12pt, top=10pt, bottom=10pt,
    enhanced,
    breakable,
    drop shadow=promptblue!40!black,
    #1
}

\begin{document}

\begin{promptframebox}
You are an expert research assistant. Produce a structured literature review summary on the topic of \textbf{[INSERT TOPIC]}. Identify \textbf{[INSERT NUMBER]} recent studies published between \textbf{[INSERT YEAR RANGE]}. For each study, provide:

\begin{enumerate}[label=\arabic*.]
    \item \textbf{Full citation} (authors, year, title, journal/source, volume/issue/pages).
    \item \textbf{Research methodology} (e.g., experimental design, meta-analysis, qualitative case study, mixed methods, longitudinal survey, RCT, systematic review).
    \item \textbf{Key findings} (stated in a clear, concise, evidence-based manner; include effect sizes or statistical significance where reported).
    \item \textbf{Identified gaps or limitations} (as noted by the authors or apparent from the study design).
    \item \textbf{Citation metrics} (minimum citation count greater than \textbf{[INSERT THRESHOLD]}).
    \item \textbf{Direct, accessible link} (DOI, PubMed ID, or stable URL) for verification.
\end{enumerate}

\textbf{Formatting requirements:} Use clean, \LaTeX-ready formatting. Avoid \verb|\section| and \verb|\subsection| commands; use hierarchical bold headings instead.

\textbf{Cross-Study Synthesis} section must address:
\begin{itemize}
    \item Common methodologies and analytical patterns
    \item Overarching findings, trends, and emergent themes
    \item Recurring gaps, limitations, and future research directions
    \item Most impactful contributions to the field
\end{itemize}

\textit{Include only verifiable, real studies from peer-reviewed sources. Maintain an academic tone throughout.}
\end{promptframebox}

\end{document}
