\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\begin{document}


\maketitle



\textbf{\large Studies Included in Synthesis}\par\vspace{0.5em}

\begin{longtable}{p{5cm}cc}
\toprule
\textbf{Study} & \textbf{Year} & \textbf{Citations} \\
\midrule
\endhead
Low-cost SDR spectrum analyzer and radio receiver ... & 2024 & 13 \\
SDR-based portable system for evaluating exposure ... & 2023 & 3 \\
Detection of Modulated Wave Transmission Failure i... & 2024 & 1 \\
SDR Testbed for RF Fingerprinting in Wireless Netw... & 2025 & 0 \\
Performance Analysis of Low-Cost AIS Receiver Usin... & 2025 & 0 \\
\bottomrule
\end{longtable}

\vspace{1em}


\textbf{\large 1. Methodological Patterns}\par\vspace{0.5em}

Across the 5 reviewed studies on HIL IOT, the following methodological patterns emerged:

- **Not specified**: 4 studies
- **Computational / Simulation**: 1 study

**Design Distribution:**
- Total experimental studies: 0
- Total meta-analyses/systematic reviews: 0
- Total longitudinal studies: 0
- Total qualitative studies: 0
- Total computational studies: 1

\vspace{1em}


\textbf{\large 2. Overarching Findings and Trends}\par\vspace{0.5em}

**Consensus Themes:**
- Multiple studies focus on: cost, radio, receiver, raspberry.

**Emergent Trends:**
- 5 recent studies (2024-2025) indicate evolving methodological approaches.

**Contradictions/Debates:**
- No major contradictions noted.

\vspace{1em}


\textbf{\large 3. Recurring Gaps and Limitations}\par\vspace{0.5em}

**Limitations noted by authors:**
- Authors of reviewed studies did not explicitly identify methodological limitations.

**Systematic gaps in the literature:**
1. Geographic scope: Most studies on HIL IOT may be concentrated in specific regions, limiting generalizability to diverse populations.
2. Methodological narrowness: The literature relies heavily on Not specified, Computational / Simulation approaches, with limited triangulation.
3. Sample and temporal constraints: Many studies use cross-sectional designs or limited sample sizes, limiting causal inference about HIL IOT.
4. Translation to practice: Limited evidence on how findings regarding HIL IOT translate into actionable interventions or policy recommendations.

\vspace{0.5em}


\begin{gapbox}[Gap 1]
Geographic scope: Most studies on HIL IOT may be concentrated in specific regions, limiting generalizability to diverse populations.
\end{gapbox}

\vspace{0.3em}


\begin{gapbox}[Gap 2]
Methodological narrowness: The literature relies heavily on Not specified, Computational / Simulation approaches, with limited triangulation.
\end{gapbox}

\vspace{0.3em}


\begin{gapbox}[Gap 3]
Sample and temporal constraints: Many studies use cross-sectional designs or limited sample sizes, limiting causal inference about HIL IOT.
\end{gapbox}

\vspace{0.3em}


\begin{gapbox}[Gap 4]
Translation to practice: Limited evidence on how findings regarding HIL IOT translate into actionable interventions or policy recommendations.
\end{gapbox}

\vspace{0.3em}


\vspace{1em}
\textbf{\large 4. Impact Assessment}\par\vspace{0.5em}

**High-Impact Studies (>$50$ citations):** 0 out of 5 reviewed studies (0%).

**Recent Contributions (2024+):** 4 studies.

**Most Cited Study:** Low-cost SDR spectrum analyzer and radio receiver using USRP N210, GNU radio, and raspberry Pi 5 (13 citations).

**Open Access Availability:** 1 of 5 studies (20%) provide open access to their full text.

\vspace{1em}


\textbf{\large 5. Future Research Directions}\par\vspace{0.5em}

Based on the identified gaps, the following research directions are recommended:

1. **Geographic scope**: Further investigation needed to address geographic scope: most studies on hil iot may be concentrated in specific regions, limiting generalizability to diverse populations..
2. **Methodological narrowness**: Further investigation needed to address methodological narrowness: the literature relies heavily on not specified, computational / simulation approaches, with limited triangulation..
3. **Sample and temporal constraints**: Further investigation needed to address sample and temporal constraints: many studies use cross-sectional designs or limited sample sizes, limiting causal inference about hil iot..
4. **Translation to practice**: Further investigation needed to address translation to practice: limited evidence on how findings regarding hil iot translate into actionable interventions or policy recommendations..

\vspace{1em}


\vfill
\begin{center}
\textit{Synthesis generated by Research Accelerant Agent on \today.}
\end{center}

\end{document}